Dear Friend Wollstein!

When you receive these lines, the three of us have solved the problem in a different way – in the way from which they have constantly tried to dissuade us. The feeling of security that you predicted for us, once we had overcome the difficulties of the move, does not want to happen at all, on the contrary: even the end is perhaps not the end!What has happened to the Jews in recent months arouses a well-founded fear that we will no longer be allowed to experience a state that is bearable for us.Tell Philippsons what you think is good, in addition to thanking them for their friendship (which is especially true for you). Please also express our heartfelt thanks to Mr. Mayer for all that he has done for us and, if necessary, would have done for us; [2] we sincerely admired his organizational achievements and successes and, had it not been for that fear, we would have gladly given ourselves into his care, which would have brought with it a feeling of relative security – unfortunately, only a relative one.We have signed a will dated Oct. 10. in 1941 our son-in-law Dr. Arthur König, Jena, Reichartsteig 14, was appointed heir. Help him as far as you can, dear friend! also help our housekeeper Minna Nickol or anyone else who asks you for it; we have to take our thanks to the grave. Maybe now the furniture, books, etc. can still be made over the 29th of Jan. (our moving date) stay in the house; perhaps Mrs. Nickol can also stay to settle the current liabilities (account of the municipal utilities, etc.). - Tax files, bank correspondence, etc., what Arthur needs, is in my study.[3] If possible, we wish to be buried with fire and enclose three explanations with this content. If not, then Mr. Mayer or Mr. Goldschmidt must probably take the necessary measures[1]. We will cover the costs as best we can; by the way, my wife was in a protestant death fund – the documents for this are in her bedroom. What is currently missing in the cost coverage will be taken over by our heir or Nora.Forgive us for causing you trouble beyond death; I am convinced that you are doing what you can do (and which may not be very much). Forgive us also our desertion! We wish you and all our friends to experience even better times.
