\documentclass[12pt]{extarticle}
%Some packages I commonly use.
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{framed}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{enumerate}
\usepackage[utf8]{inputenc}
\usepackage[top=1 in,bottom=1in, left=1 in, right=1 in]{geometry}

%A bunch of definitions that make my life easier
\newcommand{\matlab}{{\sc Matlab} }
\newcommand{\abs}[1]{|#1|}
\newcommand{\set}[1]{\{#1\}}
\newcommand{\cvec}[1]{{\mathbf #1}}
\newcommand{\rvec}[1]{\vec{\mathbf #1}}
\newcommand{\ihat}{\hat{\textbf{\i}}}
\newcommand{\jhat}{\hat{\textbf{\j}}}
\newcommand{\khat}{\hat{\textbf{k}}}
\newcommand{\minor}{{\rm minor}}
\newcommand{\trace}{{\rm trace}}
\newcommand{\spn}{{\rm Span}}
\newcommand{\rem}{{\rm rem}}
\newcommand{\ran}{{\rm range}}
\newcommand{\range}{{\rm range}}
\newcommand{\mdiv}{{\rm div}}
\newcommand{\proj}{{\rm proj}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\<}{\langle}
\renewcommand{\>}{\rangle}
\renewcommand{\emptyset}{\varnothing}
\newcommand{\attn}[1]{\textbf{#1}}
\theoremstyle{definition}
\newtheorem{theorem}{Theorem}
\newtheorem{prob}{Problem}
\newtheorem{corollary}{Corollary}
\newtheorem*{definition}{Definition}
\newtheorem*{example}{Example}
\newtheorem*{note}{Note}
\newtheorem{exercise}{Exercise}
\newcommand{\bproof}{\bigskip {\bf Proof. }}
\newcommand{\eproof}{\hfill\qedsymbol}
\newcommand{\Disp}{\displaystyle}
\newcommand{\qe}{\hfill\(\bigtriangledown\)}
\setlength{\columnseprule}{1 pt}


\title{ Math 5205 -- Topology Assignment 3}
\author{David Draguta}
\date{2021-10-18}

\begin{document}

\maketitle

\begin{exercise}
  Let $(X_{\alpha})_{\alpha \in A}$ be a non-empty family of topological spaces and $\varphi: A \to A$ a bijection of $A$ onto $A$. Prove that the cartesian product
  $\prod\limits_{\alpha \in A}X_{\alpha}$ and $\prod\limits_{\alpha \in A}X_{\varphi{\alpha}}$ are homeomorphic. 
\end{exercise}
\begin{proof}
  We define $f: \prod\limits_{\alpha \in A}X_{\alpha} \to \prod\limits_{\alpha \in A}X_{\varphi(\alpha)}$ by $ f(x) = x \circ \varphi$ and $g: f: \prod\limits_{\alpha \in A}X_{\varphi(\alpha)} \to \prod\limits_{\alpha \in A}X_{\alpha}$ by $g(x') = x' \circ \varphi^{-1}$, and check that these are continuous inverses of each other. We first check that the two are inverses of each other (which shows they're bijections)
  \begin{align*}
    g(f(x))  &= g(x \circ \varphi)     = (x \circ \varphi) \circ \varphi^{-1} = x \circ (\varphi \circ \varphi^{-1}) \\
    &= x, 
  \end{align*}
  and
  \begin{align*}
    f(g(x')) &= f(x'\circ \varphi^{-1}) = (x' \circ \varphi^{-1}) \circ \varphi = x' \circ (\varphi^{-1} \circ \varphi) \\
    &= x'.
  \end{align*}
  Next, we use Thm 101 part 3 to show that $f,g$ are continuous. For each $\alpha \in A$ and $(x_{\alpha})_{\alpha \in A} \in \prod\limits_{\alpha \in A}X_{\alpha}$ we have 
  \begin{align*}
    (\pi_\alpha \circ f)((x_{\alpha})_{\alpha \in A}) &= \pi_\alpha(f((x_{\alpha})_{\alpha \in A})) = \pi_{\alpha}((x_{\alpha})_{\alpha \in A} \circ \varphi) = \pi_{\alpha}((x_{\varphi(\alpha)})_{\alpha \in A}) = x_{\varphi(\alpha)} \\
    &= \pi_{\varphi(\alpha)}(x_{\alpha}_{\alpha \in A}),
  \end{align*}
  and so
  \begin{align*}
    \pi_{\alpha} \circ f  = \pi_{\varphi(\alpha)}
  \end{align*}
  is continous for all $\alpha \in A$. We conclude that $f$ is continuous (with respect to the weak topology).

  Similarly for $\alpha \in A$ and $(x_{\varphi(\alpha)})_{\alpha \in A} \in \prod\limits_{\alpha \in A} X_{\varphi(\alpha)}$, we have
  \begin{align*}
    (\pi_{\alpha}\circ g)((x_{\varphi(\alpha)})_{\alpha \in A}) &= \pi_{\alpha}(g((x_{\varphi(\alpha)})_{\alpha \in A})) = \pi_{\alpha}((x_{\varphi(\alpha)})_{\alpha \in A} \circ \varphi^{-1}) = \pi_{\alpha}((x_{\alpha})_{\alpha \in A}) = x_{\alpha} \\
    &= \pi_{\varphi^{-1}(\alpha)}((x_{\varphi(\alpha)})_{\alpha \in A}),
  \end{align*}
  so
  \begin{align*}
    \pi_{\alpha}\circ g = \pi_{\varphi^{-1}(\alpha)}
  \end{align*}
  is continuous for all $\alpha \in A$.
  
  Thus both $f$ and $g$ are continuous, and the two spaces are homeomorphic. 
\end{proof}
\begin{exercise}
  Let $A = B \cup C$ where $A,B,C$ are nonempty sets with $B \cap C = \emptyset$ and let $(X_{\alpha})_{\alpha \in A}$ be a family of topological spaces.
  Prove that $\prod\limits_{\alpha \in A} X_{\alpha}$ is homeomorphic to $ \prod\limits_{\alpha \in B} X_{\alpha} \times \prod\limits_{\alpha \in C} X_{\alpha}$.
\end{exercise}
\begin{proof}
  We prove 8C part 1 in the textbook.
  
  Let 
  \begin{align*}
    X = \prod\limits_{\alpha \in A} X_{\alpha}
  \end{align*}
  and
  \begin{align*}
    Y= \prod_{\lambda \in \Lambda}Y_{\lambda},
  \end{align*}
  where $Y_{\lambda} = \prod_{\alpha \in A_{\lambda}} X_{\alpha}$.

  Next, let
  \begin{align*}
    &f: X \to Y, \quad (x_{\alpha})_{\alpha \in A} \mapsto ((x_{\alpha})_{\alpha \in A_{\lambda}})_{\lambda \in \Lambda}
  \end{align*}
  and
  \begin{align*}
    &g: Y \to X, \quad ((x_{\alpha})_{\alpha \in A_{\lambda}})_{\lambda \in \Lambda} \mapsto (x_{\alpha})_{\alpha \in A}.
  \end{align*}
  These are obviously inverses. It remains to check that they're continuous. We apply part 3 of theorem 101 in the course notes.
  \begin{align*}
    \pi_{\lambda}^Y \circ f ((x_{\alpha})_{\alpha \in A}) &= \pi_{\lambda}^Y (((x_{\alpha})_{\alpha \in A_{\lambda}})_{\lambda \in \Lambda}) = (x_{\alpha})_{\alpha \in A_{\lambda}} \\
    &= (\prod\limits_{\alpha \in A_{\lambda}}\pi_{\alpha}^X )((x_{\alpha})_{\alpha \in A}),
  \end{align*}
  and so
  \begin{align*}
    \pi_{\lambda}^Y \circ f = \prod\limits_{\alpha \in A_{\lambda}}\pi_{\alpha}^X.
  \end{align*}
  To show that
  \begin{align*}
    \prod\limits_{\alpha \in A_{\lambda}}\pi_{\alpha}^X: X \to Y_{\lambda}
  \end{align*}
  is continuous, again we apply part 3 of theorem 101:
  \begin{align*}
    \pi_{\alpha}^{Y_{\lambda}} \circ \prod\limits_{\alpha \in A_{\lambda}}\pi_{\alpha}^X((x_{\alpha})_{\alpha \in A}) =\pi_{\alpha}^{Y_{\lambda} ((x_{\alpha})_{\alpha \in A_{\lambda}}) = \pi_{\alpha}^X((x_{\alpha})_{\alpha \in A}),
  \end{align*}
  and so
  \begin{align*}
    \pi_{\alpha}^{Y_{\lambda}} \circ \prod\limits_{\alpha \in A_{\lambda}}\pi_{\alpha}^X = \pi_{\alpha}^X.
  \end{align*}
  Now, for all $\alpha \in A_{\lambda}, \pi_{\alpha}^X$ is continuous, and so $\prod\limits_{\alpha \in A_{\lambda}}\pi_{\alpha}^X$ is continuous, which is true for all $\lambda \in \Lambda$. Hence, $f$ is continuous.

  For the other direction, we have
  \begin{align*}
    \pi_{\alpha}^X \circ g (((x_{\alpha})_{\alpha \in A_{\lambda}})_{\lambda \in \Lambda}) &= \pi_{\alpha}^X((x_{\alpha})_{\alpha \in A}) = x_{\alpha} \\
    &= \pi_{\alpha}^{Y_{\lambda}} \circ \pi_{\lambda}^Y (((x_{\alpha})_{\alpha \in A_{\lambda}})_{\lambda \in \Lambda}),
  \end{align*}
  and so
  \begin{align*}
    \pi_{\alpha}^X \circ g = \pi_{\alpha}^{Y_{\lambda}} \circ \pi_{\lambda}^Y,
  \end{align*}
  where the right hand side is a composition of continuous functions, and is therefore continuous. By theorem 101 part 3 we conclude that $g$ is continuous. Hence $X$ is homeomorphic to $Y$.

  Now, partitioning $A$ into $A_{1} = B$ and $A_{2} = C$ and applying this result yields the solution to the problem. 
\end{proof}

\begin{exercise}
  \begin{enumerate}
  \item
    Suppose that the topology $\tau$ on $X$ is the weak topology induced by a family $(f_{\alpha})_{\alpha \in A}$ of functions $f_{\alpha}: X \to X_{\alpha}$ and let
    $f: Y \to X$, where $Y$ is a topological space. Prove or disprove: if for each $\alpha \in A$, $f_{\alpha} \circ f$ is continuous at $y_0 \in Y$,
    then $f$ is continuous at $y_0$.
  \item
    Suppose that the topology $\tau$ on $X$ is the quotient topology induced by a surjection $h:Z \to X$ and $f:X \to Y$, where $Y$ is a topological space.
    \begin{enumerate}
    \item
      Prove or disprove: if $z_0 \in Z, h(z_0) \in U \subseteq X$, and $h^{-1}(U)$ is a nhood of $z_0$ in $Z$, then $U$ is a nhood of $h(z_0)$ in $X$.
    \item
      Prove or disprove: if $z_0 \in Z$ and $f \circ h$ is continuous at $z_0$, then $f$ is continuous at $h(z_0)$. 
    \end{enumerate}
  \end{enumerate}
\end{exercise}
\begin{proof}
  \begin{enumerate}
  \item
    Let $V \subseteq X$ be a nhood of $f(y_0)$ in $X$. Let $\mathcal{B}_{f_{\alpha}(f(y_0))}^{\alpha}$ be a nhood base at $f_{\alpha}(f(y_0))$ in $X_{\alpha}$ for each $\alpha \in A$.
    Then there exist $V_i \in  \mathcal{B}_{f_{\alpha_i}(f(y_0))}^{\alpha_i}$ such that 
    \begin{align*}
      f_{\alpha_1}^{-1}(V_1) \cap \dots \cap f_{\alpha_n}^{-1}(V_n) \subseteq V.
    \end{align*}
    We have
    \begin{align*}
      f^{-1}(f_{\alpha_1}^{-1}(V_1) \cap \dots \cap f_{\alpha_n}^{-1}(V_n))
      &= f^{-1}(f_{\alpha_1}^{-1}(V_1)) \cap \dots \cap f^{-1}(f_{\alpha_n}^{-1}(V_n)) \\
      &= (f_{\alpha_1} \circ f)^{-1}(V_1) \cap \dots \cap (f_{\alpha_n} \circ f)^{-1}(V_n).
    \end{align*}
    Now, as $f_{\alpha_i} \circ f$ is continuous at $y_0$ and $(f_{\alpha_i} \circ f)(y_0) \in V_i$ is open in $X_{\alpha_i}$, we have that $y_0 \in (f_{\alpha_n} \circ f)^{-1}(V_i)$ is open in $X$, too, for each $i$. Thus, $y_0 \in (f_{\alpha_1} \circ f)^{-1}(V_1) \cap \dots \cap (f_{\alpha_n} \circ f)^{-1}(V_n)$ is open in $Y$, and 
    \begin{align*}
      (f_{\alpha_1} \circ f)^{-1}(V_1) \cap \dots \cap (f_{\alpha_n} \circ f)^{-1}(V_n) \subseteq f^{-1}(V).
    \end{align*}
    Hence, $f^{-1}(V)$ is a nhood of $y_0$ in $Y$ such that $f(f^{-1}(V)) \subseteq V$, and $f$ is continuous at $y_0$. 
  \item
    \begin{enumerate}
    \item
      If $h^{-1}(U)$ is a nhood of $z_0$ in $Z$, then there exists some open $z_0 \in W \subseteq Z$.
      Since $h$ is surjective we have $W=h^{-1}(h(W))$, so by the definition of the quotient topology $h(W)$ is open in $X$.
      Since $h(z_0) \in h(W) \subseteq U$, we conclude that $U$ is a nhood of $h(z_0)$ in $X$.
    \item
      Let $V$ be a nhood of $f(h(z_0))$. Then, as $f \circ h$ is continuous at $z_0$ there exists a nhood $W$ of $z_0$ such that $(f \circ h)(W) \subseteq V$.
      Then, as $W = h^{-1}(h(W))$ (since $h$ is surjective), by the first part of this question we conclude $h(W)$ is a neighbourhood of $h(z_0)$.
      Thus, $f$ is continuous at $h(z_0)$ (since $f(h(W)) \subseteq V$). 
    \end{enumerate}
  \end{enumerate}
\end{proof}
\begin{exercise}
  Show that TFCAE for a topological space $(X, \tau)$:
  \begin{enumerate}
  \item
    If $E \subseteq X$ and $x \in \overline{E}$, then there is a sequence $(x_n)_{n=1}^{\infty}$ in $E$ with $x_n \to x$.
  \item
    If $x \in U \subseteq X$ and for every sequence $(x_n)_{n=1}^{\infty}$ in $X, x_n \to x$ implies that $(x_n)_{n=1}^{\infty}$ is eventually in $U$, then $x \in U^o$.
  \item
    If $f:X \to Y$ where $Y$ is a topological space, $x \in X$ and for every sequence $(x_n)_{n=1}^{\infty}$ in $X$, $x_n \to x$ implies $f(x_n) \to f(x)$,
    then $f$ is continuous at $x$. 
  \end{enumerate}
\end{exercise}

\begin{proof}
  \begin{itemize}
  \item
    $1. \implies 2.$
    
    If $x \not \in U^o$, then for every neighbourhood $W$ of $x$ we have, $(W \setminus \set{x}) \cap U^c = W\cap (U^c \setminus \set{x}) = W \cap U^c \neq \emptyset$,
    so that $x \in (U^c)' \subseteq \overline{U^c}$. Thus, there exists a sequence $(x_n)_{n \in \N}$ in $U^c$ with $x_n \to x$, i.e. there exists a sequence of points converging to $x$ that is not eventually in $U$. 
  \item
    $2. \implies 3.$
    
    Let $V \subseteq Y$ be a nhood of $f(x)$. Then for any sequence $x_n \to x$ we have $f(x_n) \to f(x)$, so that $(f(x_n))_{n \in \N}$ is residually in $V$,
    and $(x_n)_{n \in N}$ is residually in $f^{-1}(V)$. Thus, we have that $x \in (f^{-1}(V))^o \subseteq f^{-1}(V)$. Let $W:=f^{-1}(V)$. Then $W$ is a nhood of $x$,
    and $f(W) \subseteq V$, so that $f$ is continuous. 
  \item
    $3. \implies 2.$

    Well, if any sequence $(x_n)$ in $X$ is eventually in $U$ then $1_U:X \to \set{0,1}$, i.e. the indicator function for $U$ is continuous at $x$, and so
    giving $\set{0,1}$ the Sierpinski topology, we have for $\set{1}$ some neighbourhood $W$ of $X$ such that $1_U(W) \subseteq \set{1}$, but that means $W \subseteq U$,
    and so $x \in W^o \subseteq U^o$.

    $2. \implies 1.$

    If $x \in E^o$, then as this is a neighbourhood of $x$, any $x_n \to x$ will be eventually in $E^o$, and we can take our sequence as the tail of any sequence.
    Otherwise, $x \not \in E^o$ implies $x \in \overline{E} \setminus E^o = Fr(E) = \overline{E} \cap \overline{X \setminus E}$, i.e. $x \in \overline{X \setminus E}$,
    but $x \not \in (\overline{X \setminus E})^o = (X \setminus E)^o$, so by $2$ there exists a sequence $(y_n)$ such that for any $n_0 \in \N$ there exists some $n > n_0$ such
    that $y_n \not \in X \setminus E$. Then we can form a subsequence $(x_n)_{n \in \N}$ such that for each $n \in \N$ there exists some $k \in \N$ with $x_n = y_{n_k}$,
    where $y_{n_k} \not \in X \setminus E$, i.e. $y_{n_k} \in E$ and $n_k < n_{k+1}$ for each $k$. Then $x_n \to x$ and $(x_n)_{n \in \N}$ is entirely in $E$. 
     
  \end{itemize}
\end{proof}
\begin{exercise}
  \begin{enumerate}
  \item
    From 10A, p.72 in the text: Answer questions, a), b), c) for the topological space described in 2 (the cocountable topology).
  \item
    Find an example of two distinct topologies, $\tau$ and $\sigma$, on the same set $X$ which have the same convergent sequences. Find an example of a discontinuous function $f:(X, \tau) \to (X, \sigma)$ which is sequentially continuous. 
  \end{enumerate}
\end{exercise}
\begin{proof}
  \begin{enumerate}
  \item
    \begin{enumerate}
    \item
      The open sets in this topology are the uncountable sets.

      Let $x \in X$, $U \in \mathcal{U}_x$, and $(x_n)_{n \in \N}$ a sequence in $X$ such that $x_n \to x$.
      Then as $U^o \subseteq U$, we have that $U$ is uncountable. Suppose that $(x_n)_{n \in \N}$ doesn't stabilize on $x$,
      that is for any $n_0 \in \N$ there exists some $n \geq n_0$ such that $x_n \neq x$.

      Let
      \begin{align*}
        I := \set{n \in \N: x_n \neq x}.
      \end{align*}
      Then $I$ is countable and unbounded, and $U^* = U \setminus (x_n)_{n \in I}$ is a neighbourhood of $x$; but $(x_n)_{n=1}^{\infty}$
      is not residually in $U^*$, and that's a contradiction.

      Okay, so the sequences in this topology are those that stabilize, i.e. those such that there exists some $n_0 \in \N$ such that $x_n = x$ for all $n \geq n_0$. What can we say about the points to which the sequences converge?

      There must not be a countably infinite neighbourhood base at $x$. If there is such a base, we have $\mathcal{B}_x = \set{U_n : n \in \N}$, and we can put $V_n := \bigcap\limits_{k=1}^n U_k$,
      and use this to define a sequence by choosing some $x_n \in V_n$ such that $x_n \neq x$ for all $n \in \N$. Then $x_n \to x$ and $ V_1^* := V_1 \setminus (x_n)_{n=1}^{\infty}$ is an nhood of $x$ (it's uncountable and we chose the $x_n \neq x$),
      so that $(x_n)_{n=1}^{\infty}$ is residually in $V_1^*$, a contradiction. Clearly no neighbourhood base can be finite, because we're in an uncountable space where the open sets are uncountable. Hence,
      it must be that any neighbourhood base at $x$ must be uncountable. 


    \item
      Suppose that $X$ is first countable. Let $x \in \X$, and $\mathcal{B}_x$ be a countable nhood base at $x$ in $X$.
      Then $\bigcap \mathcal{B}_x$ is a countable intersection of non-disjoint uncountable sets, and so is uncountable, hence open.
      Let $B = \bigcap \mathcal{B}_x \setminus \set{y}$, where $y \neq x$ and $y \in \bigcap \mathcal{B}_x$. Then, there exists some $W \in \mathcal{B}_x$
      such that $W \subseteq B$, which is impossible, as $y \in W$, so $y$ both is and is not part of the intersection.
      Hence, $X$ is not first countable.
    \item
      No, because $(x_n) \subseteq E$ would have to stabilize on $x$, but $x$ in general need not be in $E$, i.e. there exists $n \in \N$ such that $x_n=x$, but it could be that $x \in \overline{E} \setminus E$.

    \end{enumerate}
  \item
    We take $X = \R^{\R}$, $\tau$ the tychonoff topology on $X$, $\sigma$ the box topology on $X$, and $f$ the identity function $f = id: (X, \tau) \to (X, \sigma)$. Then $f$ is sequentially continuous, but $\sigma$ is strictly
    finer than $\tau$, so there exists some open $U \in \sigma \setminus \tau$. Hence, $U = f^{-1}(U) \subseteq (X, \tau)$ is not open, so that $f$ is not continuous. 


    

  \end{enumerate}
\end{proof}
\end{document}



